Letter to the Editor

### 2022-06-23 editorial-communication/cover-letter-submission.Rmd

Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.

>>>>

Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
Also, we believe our manuscript complements a recently published manuscript in *Nature Ecology and Evolution*. In the manuscript, Gallagher et al. (2020) outline how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology. A key component of Open Science is the ability to collaboratively contribute to and share code and data--platforms like GitHub provide an free and accessible platform to do just that.
